A Type System for Safe and Scalable Parallelism using Logical Regions

### 2012-07-05 doc/popl2013/legion-types.tex
Creating a separate tex file for the introduction
Fixing a number in the abstract and adding an evaluation section
Fixing some typos in the abstract

\title{A Type System for Safe and Scalable Parallelism using Logical Regions}
%\title{Scalable and Safe Parallelism using Logical Regions}
\authorinfo{}{}{}
\maketitle

\begin{abstract}
Legion is a programming model that introduces 
{\em logical regions} as a mechanism for targeting large heterogeneous machines 
with complex memory hierarchies.  Logical regions are a first-class 
feature of Legion that allow programmers to specify independence 
and locality properties of program data dynamically.  We present
a type and effect system for reasoning about logical regions in Legion.  
We prove a soundness result for our type system and use it to show
that all memory accesses in Legion are safe.  Futhermore, we prove that
the soundess of our type system enables a scalable hierarchical
scheduling algorithm for Legion programs.  We implement a type checker
for Legion programs and improve performance up to 85\% by eliding
unncessary memory checks.  We demonstrate an implementation of the Legion 
runtime based on the hierarchical scheduling algorithm scales for
three real-world applications.

@@

\section{Introduction}
\label{sect:intro}
Introduction goes here.

@@

>>>>

\title{A Type System for Safe and Scalable Parallelism using Logical Regions}
%\title{Scalable and Safe Parallelism using Logical Regions}
\authorinfo{Sean Treichler \and Michael Bauer \and Alex Aiken}{Stanford University}{\{sjt,mebauer,aiken\}@cs.stanford.edu}
%\authorinfo{Sean Treichler}{Stanford Unviersity}{sjt@cs.stanford.edu}
%\authorinfo{Michael Bauer}{Stanford University}{mebauer@cs.stanford.edu}
%\authorinfo{Alex Aiken}{Stanford University}{aiken@cs.stanford.edu}
\maketitle

\begin{abstract}
Legion is a programming model that introduces 
{\em logical regions} as a mechanism for targeting large heterogeneous machines 
with complex memory hierarchies.  Logical regions are a first-class 
feature of Legion that allow programmers to specify independence 
and locality properties of program data dynamically.  We present
a type and effect system for reasoning about logical regions in Legion.  
We prove a soundness result for our type system and use it to show
that all memory accesses in Legion are safe.  Furthermore, we prove that
the soundness of our type system enables a scalable hierarchical
scheduling algorithm for Legion programs.  We implement a type checker
for Legion programs and improve performance up to 71\% by eliding
unnecessary memory checks.  We demonstrate an implementation of the Legion 
runtime based on the hierarchical scheduling algorithm scales for
three real-world applications.

@@

\input{intro}

@@

\input{evaluation}

\input{related}
